XXXXX

### 2014-12-24 paper/RDF validation requirements/RDF validation requirements.tex
corrected DL of cardinality restrictions
added mapping tables

@@

@@

Assume that  mentorOf and studentOf are inverse properties.\\
\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
\end{DL}

\textcolor{red}{corrections (to verify):}

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 studentOf^{-}.\top \sqcap \leq2 studentOf^{-}.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 studentOf^{-}.\top $
\end{DL}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
\end{DL}
\subsection{Complex Example}

@@

%\tb{ToDO: add DL}
\noindent Taking mentorOf and studentOf as inverse properties. \\
\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
\end{DL}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
\end{DL}

@@

%\tb{ToDO: add DL}
\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
\end{DL}
\section{Exact Qualified Cardinality Restrictions on Properties}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
\end{DL}

@@

\begin{DL}
parentOf $\equiv$ $childOf^{-}$ \\
not sure if this should be rather\\
$parentOf \sqsubseteq childOf^{-}$ \\
\end{DL}

\begin{gcotable}
property & parentOf & childOf & - & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

consistent with ontology:

\begin{gcotable}
property & $\top$ & parentOf & childOf & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

@@

@@

\begin{gcotable}
property & ancesterOf & ancestorOf, ancestorOf & - & $\top$ & transitive role \\
\end{gcotable}

syntactic sugar (ontology conform):

\begin{gcotable}
property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & transitive role \\
\end{gcotable}

without syntactic sugar (ontology conform):

\begin{gcotable}
property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
\end{gcotable}

@@

\begin{DL}
$marriedTo \sqsubseteq marriedTo^{-}$ \\
\end{DL}

\begin{gcotable}
property & marriedTo & marriedTo & - & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

ontology conform:

\begin{gcotable}
property & $\top$ & marriedTo & marriedTo & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & marriedTo & - & $\top$ & symmetric role \\
\end{gcotable}

@@

\begin{DL}
$parentOf \sqsubseteq \neg parentOf^{-}$ or\\
$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$
\end{DL}

\begin{gcotable}
property & $parentOf^{-}$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
property & parentOf & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
\end{gcotable}

ontology conform:

\begin{gcotable}
property & $\top$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
property & $\top$ & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & parentOf & - & $\top$ & asymmetric role \\
\end{gcotable}

@@

\section{Class-Specific Reflexive Object Properties / Local Reflexivity}

@@

\begin{DL}
$\exists$ talksTo .Self. 
\end{DL}

@@

\begin{gcotable}
property & $\exists$ talksTo .Self.  & talksTo & - & Self & $\exists$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\exists$ talksTo .Self. & talksTo & - & - & reflexive role \\
\end{gcotable}

\section{Reflexive Object Properties / Global Reflexivity}

@@

@@

\begin{gcotable}
property & $\top$ & knows & - & $\top$ & reflexive role \\
\end{gcotable}

\begin{gcotable}
property & $\top$ & knows & - & Self & $\exists$ \\
\end{gcotable}

@@

@@

\begin{gcotable}
property & $\top$ & marriedTo & - & $\top$ & irreflexive role \\
\end{gcotable}

\begin{gcotable}
property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ \\
class & $\top$ & - & - & $\exists$ marriedTo . Self & $\neg$ \\
\end{gcotable}

@@

Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\

>>>>

%\newenvironment{gcotable}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
	%\begin{center}
  %\begin{tabular}{l|l|l|l|l|l|l}
  %\hline
  %\textbf{c. type} & \textbf{context c. $\vert$ p.} & \textbf{left r. list} & \textbf{right r. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  %\hline
%
%}{
  %\hline
  %\end{tabular}
	%\end{center}
%}

@@

syntactic sugar (preferred):

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.\top \sqcap \leq2 mentorOf.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.\top $
\end{DL}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.Jedi \sqcap \leq2 mentorOf.Jedi $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.Jedi $
\end{DL}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.\top \sqcap \leq2 mentorOf.\top $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.\top $
\end{DL}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.Jedi \sqcap \leq2 mentorOf.Jedi $\\
$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.Jedi $
\end{DL}

@@

\begin{DL}
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
\end{DL}

\section{Exact Qualified Cardinality Restrictions on Properties}

@@

\begin{DL}
$Jedi \sqsubseteq \exists attitude.\{good\} $\\
$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
\end{DL}

@@

\begin{DL}
$parentOf \equiv childOf^{-}$ \\
\end{DL}

outdated:

\begin{gcotable}
property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
\end{gcotable}

\begin{DL}
captainOf $\equiv$ hasCaptain$^{-}$ \\
\end{DL}

\begin{gcotable}
property & $\top$ & captainOf & hasCaptain & - & inverse \\
\end{gcotable}

alternative:

\begin{gcotable}
property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
\end{gcotable}

alternative:

\begin{gcotable}
property & captainOf & hasCaptain & - & - & inverse \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & ancestorOf, ancestorOf & ancestorOf & - & $\sqsubseteq$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & ancestorOf & - & - & transitive \\
\end{gcotable}

@@

\begin{DL}
$marriedTo \equiv marriedTo^{-}$ \\
\end{DL}

\begin{gcotable}
property & $\top$ & marriedTo & marriedTo & - & inverse \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & marriedTo & - & - & symmetric \\
\end{gcotable}

@@

\begin{DL}
$parentOf \sqsubseteq \neg parentOf^{-}$ or\\
$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$ or \\
disjoint(parentOf, parentOf$^{-}$)
\end{DL}

\begin{gcotable}
property & $\top$ & $parentOf^{-}$ & parentOf & - & inverse \\
property & $\top$ & parentOf & $parentOf^{-}$ & - & $\ne$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & parentOf & - & - & asymmetric \\
\end{gcotable}

@@

\section{Class-Specific Reflexive Object Properties}

@@

\begin{DL}
TalkingToThemselves $\sqsubseteq$ $\exists$ talksTo .Self. 
\end{DL}

@@

\begin{gcotable}
property & TalkingToThemselves & talksTo & - & Self & $\exists$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\exists$ talksTo .Self & talksTo & - & - & reflexive \\
\end{gcotable}

\section{Reflexive Object Properties}

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\top$ & - & - & $\top$, $\exists$ knows . Self & \sqsubseteq \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & knows & - & - & reflexive \\
\end{gcotable}

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & \sqsubseteq \\
\end{gcotable}

@@

\begin{gcotable}
property & $\top$ & marriedTo & - & - & irreflexive \\
\end{gcotable}

@@

Literal Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

### 2014-12-24 paper/paper 2/paper 2.tex
corrected DL of cardinality restrictions
added mapping tables

>>>>

\section{Syntactic Sugar}

In Section 1.3 we introduced three forms of RBox axioms: role inclusions, role equiv-
alences and role disjointness. OWL provides a variety of others, namely role transi-
tivity, symmetry, asymmetry, reflexivity and irreflexivity. These are sometimes consid-
ered as basic axiom types in DLs as well, using some suggestive notation such as
Trans( ancestorOf ) to express that the role ancestorOf is transitive. However, such axioms
are just syntactic sugar; all role characteristics can be expressed using the features
of DLs that we have already introduced.

\begin{itemize}
  \item domain and range
	\item (ir)reflexive object properties
	\item Exact Qualified Cardinality Restrictions on Properties
\end{itemize}
